% @article{viola2001rapid,
%   title={Smart E-Ticketing System for Public Transport Bus},
%   author={S. Kazi, M. Bagasrawala, F. Shaikh and A. Sayyed},
%   journal={2018 International Conference on Smart City and Emerging Technology (ICSCET), Mumbai, 2018.},
%  }

\new [1] S. Kazi, M. Bagasrawala, F. Shaikh and A. Sayyed, ”Smart E-Ticketing System for Public Transport Bus,” 2018 International Conference on Smart City and Emerging Technology (ICSCET), Mumbai, 2018. 
\new[2] Saurabh C. and Balram T. ”Public transport system ticketing system using RFID and ARM processor Perspective Mumbai bus facility B.E.S.T,” 2014 International Journal of Electronics and Computer Science Engineering ISSN- 2277- 1956, 
\new[3] S. Karthick. and A. Velmurugan., ”Android suburban railway ticketing with GPS as ticket checker,” 2012 IEEE International Conference on Advanced Communication Control and Computing Technologies (ICACCCT). 
\new[4] Shital Kotle, Korke Jayshree D., Kandharkar Snehal B., Gaikwad Pranali A. and Kale Geetanjali J., ”Smart Bus Ticketing Destination Announcement System Using QR-Code,” 11th International Conference on Recent Innovations in Science, Engineering and Management, ISBN:978-93-87793-19-4, 2018. 
\new[5] V. Malathi, B. Balamurugan and S. Eshwar, ”Achieving Privacy and Security Using QR Code by Means of Encryption Technique in ATM,” 2017 Second International Conference on Recent Trends and Challenges in Computational Models (ICRTCCM). 
\new[6] P. Telluri, S. Manam and J. M. Oli, ”Automated Bus Ticketing System Using RFID,” 2019 2nd International Conference on Intelligent Computing, Instrumentation and Control Technologies (ICICICT). 
\new[7] V. Ceronmani Sharmila, S. Monesh, R. Aayush, G. Karesh and I.Ibrahim, ”Digitized Bus Ticketing Framework,” 2019 1st International Conference on Innovations in Information and Communication Technology (ICIICT). 
\new[8] K. Hargunani, P. Kengar, M. Lokhande, R. Gawade and S. K. More,”Integrated Bus System Using QR Code,” 2018 Fourth International Conference on Computing Communication Control and Automation (ICCUBEA). 
\new[9] R. B. Torode, ”Prestige-contactless smartcard ticketing on London Transport,” 1996 International Conference on Public Transport Electronic Systems (Conf. Publ. No. 425), London, UK, 1996. 
\new[10] M. Arora, C. Kumar and A. K. Verma, ”Increase Capacity of QR Code Using Compression Technique,” 2018 3rd International Conference and Workshops on Recent Advances and Innovations in Engineering (ICRAIE)



% @misc{bworld,
%   author = {Ingo Lütkebohle},
%   title = {{BWorld Robot Control Software}},
%   howpublished = "\url{http://aiweb.techfak.uni-bielefeld.de/content/bworld-robot-control-software/}",
%   year = {2008}, 
%   note = "[Online; accessed 19-July-2008]"
% }
