\documentclass{SNJB}
\usepackage{babel}
\usepackage{babel}
\usepackage{algorithm}
\usepackage{algorithmic}

\usepackage{caption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{fancybox}

\usepackage{url}
\usepackage[breaklinks=true]{hyperref}

\usepackage[]{nomencl}
\renewcommand{\nomname}{Abbreviations}
\makenomenclature

\makeindex

\begin{document}

\title{Smart Bus System}
\author{Sharma Sagar Ganesh}

\newauthor{prof.Y.K.Desai}

\new{Name: Sharma Sagar Ganesh  \\ \new{1.5cm} Seat No. : T190414329}

\dept{Computer Engineering }
\supervisor{Prof.Y.K.Desai}
\submitdate{Nov-Dec, 2022-23}
\degree{Bachelor of Engineering}
\specialization{Computer}
\type{Seminar Report}
%\type{Seminar}
\hod{Prof.K.M.Sanghavi}
\principal{Dr.M.D.Kokate}
\beforepreface
%\end{tabular}

\titleformat{\chapter}[display]
{\centering\normalfont\huge\bfseries}
{\chaptertitlename\ \thechapter}{20pt}{\Huge}


\thisfancyput(-0.0in,-10.0in){%
	%\thisfancypage{%
%\setlength{\fboxrule}{1pt}\doublebox}{}
\setlength{\unitlength}{1in}\framebox(6.7,10.2)}

\prefacesection{Acknowledgement}

%\input{acknowledgement}
I would like to acknowledge all the people who have been of help and assisted me throughout my Seminar Work. First of all I would like to thank my respected guide Prof. Y. K. Desai (Assistant Professor in Department of Computer Engineering at SNJB’s College of Engineering) for introducing me to the features needed. The time to time guidance, encouragement and valuable suggestions received from her are unforgettable in my life. This work would not have been possible without the enthusiastic response, insight, and new ideas from her.
	
I am also grateful to all my faculty members of SNJB’s Late Sau. Kantabai Bhavarlalji Jain College of Engineering, for their support and cooperation.

I would like to thank my lovely parents for time to time support and encouragement and valuable suggestions, and thank my friends for their valuable support and encouragement. The acknowledgement would be incomplete without mention of the blessings of the Almighty which helped me in keeping high during the most difficult period.


\acknowledgeauthor


\newpage
\thisfancyput(-0.0in,-10.0in){
%%\thisfancypage{%
%\setlength{\fboxrule}{1pt}\doublebox}{}
\setlength{\unitlength}{1in}\framebox(6.7,10.2)}
\prefacesection{Abstract}
\emph{
Public transport is the affordable and most trustable transportation system in India, hence it has always been popular with the millions. Buses are an integral means of public trans- port which plays a vital part in transportation in India. The improvement in the transport system has been adding in day- to- day life as further and further people depend on public transport to go to work, academy, hospitals, etc. Even though the public transport buses have been delivering fairly satisfactory services, there's a need for a smart and responsible system. The major problem in regional buses is about issuing bus tickets, which frequently leads to conflict between the passenger and the conductor. keeping this in mind, we're developing an android application which will deliver an effective and smooth bus ticketing experience for both the user( passenger) and the service provider( conductor). The android application provides an interface for the bus ticketing system associated with the technology of QR Code for quick money transfer. QR Code or the Quick Response Code is the most dominant form of storing and swapping information between devices. It’s a class of matrix BarCode and has further capacity than UPC Codes. generally scrutinised and interpreted by a camera enabled smartphone, but also can be interpreted or generated by any camera device enforced with QR decrypting sense. The passengers can go cashless using this application, and the conductor doesn't have to worry about returning change for the paid bus fare. By this application, we can minimise the operation of paper tickets which will also support in green India.
The need for a real- time public transport information system is promoting steadily. People want to plan their metropolis commutes and don't like staying for long hours, nor take a lengthy path to reach their destination. The suggested hardware result in this report computes the shortest route to reach the destination in real time and gives that information to the bus driver. Artificial Neural Networks( ANN) is applied to give an accurate estimate of the arrival time( ETA) to the commuter by means of an application. ETA to the coming stop is conveyed to the commuter using the MQTT( Message Queuing Telemetry Transport) protocol, by the hardware mounted on the bus. The proposed result also adds a line regulation console to the administrants, making them manage and watch the line of buses in real time. The prototype therefore developed makes sure the commuting in metropolises is pleasant, and hassle free.
}

% Use following command at the command prompt to display the Abbreviations
% makeindex report.nlo -s nomencl.ist -o report.nls
%\newpage
%\addcontentsline{toc}{chapter}{List of Abbreviations}
%\printnomenclature
\newpage
\thisfancyput(-0.0in,-10.0in){%
	%\thisfancypage{%
%\setlength{\fboxrule}{1pt}\doublebox}{}
\setlength{\unitlength}{1in}\framebox(6.7,10.2)}

\afterpreface

% \newpage
% \thisfancyput(-0.0in,-10.0in){%
	%\thisfancypage{%
%\setlength{\fboxrule}{1pt}\doublebox}{}
% \setlength{\unitlength}{1in}\framebox(6.7,10.2)}
% \listoftables

\newpage
\thisfancyput(-0.0in,-10.0in){%
	%\thisfancypage{%
%\setlength{\fboxrule}{1pt}\doublebox}{}
\setlength{\unitlength}{1in}\framebox(6.7,10.2)}
\listoffigures
%\input{glossary}
\clearpage
\pagenumbering{arabic}
\pagestyle{plain}


\pagestyle{fancy}
\titleformat{\chapter}[display]
{\flushright\normalfont\huge\bfseries}
{\chaptertitlename\ \thechapter}{20pt}{\Huge}



\chapter{Introduction}
\input{./intro}

\chapter{Problem Statement}
\input{./ProbStat}

\chapter{Literature Survey}
\input{./lits}

\chapter{EXISTING METHOD}
\input{./Exmethod}

\chapter{PROPOSED SYSTEM}
\input{./Psystem}
%\newpage

\chapter{Conclusion }
\input{./conclusion}

\titleformat{\chapter}[display]
{\centering\normalfont\huge\bfseries}
{\chaptertitlename\ \thechapter}{20pt}{\Huge}

%\prefacesection{Conclusion }
%\chapter{Conclusion}
%\input{./conclusion}
%%%%%\appendix
%\input{appendix}

%\nocite{*}
% \renewcommand{\bibname}{References}
% \bibliographystyle{IEEEtran}
% \bibliography{ref1}
\chapter{References}
\input{./ref1}

\titleformat{\chapter}[display]
{\centering\normalfont\huge\bfseries}
{\chaptertitlename\ \thechapter}{20pt}{\Huge}

\chapter{Report Documentation}
\input{./ReDocu}

%Use following command at the command prompt to display the Index
% makeindex thesis
%%%%%\newpage
%%%%%\addcontentsline{toc}{chapter}{Index}
%%%%%\printindex

\end{document}
